True versus apparent shapes of astrophysical bow shocks

### 2015-07-02 papers/Paper1/sec-conic.tex
01/07/15 Last advance to conic section until edition.

With $\tan\theta_c\equiv \frac{b}{a}$,  $f(i;\theta_c)\equiv\left(1-\tan^2\theta_c\tan^2i\right)^{1/2}$ and introducing the
radius of curvature $R_c\equiv \frac{b^2}{a}$ we find that:

\begin{align}
\frac{R'_0}{D'}={R_0}{D}\left(1-A\cot^2\theta_c(f(i;\theta_c)-1) \right)
\end{align}

Where $A\equiv \frac{R_c}{R_0}$
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proplyd-bowshocks"
%%% End:

>>>>

With $\tan\theta_c\equiv \frac{b}{a}$,  $f(i;\theta_c)\equiv\left(1\pm\tan^2\theta_c\tan^2i\right)^{1/2}$ and introducing the
radius of curvature $R_c\equiv \frac{b^2}{a}$ we find that:

\begin{align}
\frac{R'_0}{D'}={R_0}{D}\left(1+A\cot^2\theta_c(f(i;\theta_c)-1) \right)
\end{align}

Where $A\equiv \frac{R_c}{R_0}$

The Radius of curvature in the observer's frame is given by $R'_c=\frac{b'^2}{a'^2}$. Then:

\begin{align}
\frac{R'_c}{R'_0} = \frac{A}{\cos^2 i f(i;\thet_c)\frac{q'}{q}}
\end{align}

Where $q=\frac{R_0}{D}$ and $q' = \frac{R'_0}{D'}$
%Insert figures where needed

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proplyd-bowshocks"
%%% End:
